COG-ED Manuscript

### 2021-09-09 06_Paper/COG-ED/Manuscript.Rmd
changed file name of flag file

  here::i_am("flag_project_root_COGERED.txt")

@@

  data_quest <- read.csv(here("04_RawData", "Sampledata", "CERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
  colnames(data_quest)[1] <- "set" # rename the first column

>>>>

  here::i_am("flag_project_root_CERED.txt")

@@

  data_quest <- read.csv(here("04_RawData", "Sampledata", "COGED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
  colnames(data_quest)[1] <- "set" # rename the first column
